Estimation of Intracortical Connectivity in a Dynamical Neural Field Model

### 2010-06-23 ltx/PLoS/LaTeX_Manuscript.tex
updated tables

\begin{table}[!ht]
\caption{
\bf{Notation and Parameters}}
\begin{tabular}{|c|c|c|c|}
	\hline
	\textbf{Symbol} & \textbf{Quantity} & \textbf{Value} & \textbf{Units}\\
	\hline
\multicolumn{4}{|c|}{\emph{Domain and indices}}\\
\hline
$\Omega$ & spatial domain & &\\
$t$ & time & & seconds\\
$\mathbf{r}$ & spatial location & &\\
$n$ & sensor index $n=1,..,N$ & &\\
$T_s$ & time step & $0.001$ & seconds\\
$T$ & number of time steps & 0.4 & seconds\\
\hline
\multicolumn{4}{|c|}{\emph{Spatiotemporal signals}}\\
\hline
    $y(\mathbf{r}_n,t)$ & observation & & mV\\
    $v(\mathbf{r},t)$ & mean membrane potential & & mV \\
	$g(\mathbf{r},t)$ & weighted firing rate function & & \\
	$f(\mathbf{r},t)$ & firing rate function & & spikes.s$^{-1}$\\
	$e(\mathbf{r},t)$ & field disturbance, (covariance $\gamma$) & &\\
	$\varepsilon(\mathbf{r}_n,t)$ & observation noise, (covariance $\Sigma_\epsilon$) & &\\
\end{tabular}
\begin{flushleft}Table caption
\end{flushleft}
\label{tab:label}
\end{table}

@@

% 
% \begin{table}[h!]\footnotesize
%     \begin{tabular}{ll}
%         	$h(t)$ & post-synaptic response kernel \\
% 	$m(\mathbf{r},\mathbf{r}')$ & sensor kernel, width $\sigma_m^2$ \\
% 	$\eta(t)$ & Heaviside function \\
% 	$\zeta$ & inverse synaptic time constant \\
% 	$w(\mathbf{r},\mathbf{r}')$ & spatial connectivity kernel \\
% 	$f_{max}$ & maximal firing rate \\
% 	$\varsigma$ & slope of sigmoidal activation function \\
% 	$v_0$ & firing threshold \\
% 	$\delta(t)$ & Dirac-delta function \\
% 	$D$ & Temporal differential operator \\
% 	$\xi$ & time constant parameter
%     \end{tabular}
%     \caption{Model}
% \end{table}
% 
% \begin{table}[h!]\footnotesize
%     \begin{tabular}{ll}
%         $L$ & number of field basis functions  \\
%     	$\mathbf{\phi(r)}$ & vector of Gaussian basis functions \\
%     	$\mathbf{x}_t$ & state vector at time $t$ \\
%     	$\mathbf{\psi}$ & vector of connectivity kernel basis functions \\
%     	$\theta$ & vector of connectivity kernel parameters \\
%     	$\Gamma$ & inner product of field basis functions \\
%     	$q()$ & state function \\
%     	$Q()$ & state function \\
% 	$\gamma(\mathbf r-\mathbf r')$& field disturbance covariance function\\
%     	$\mathbf{e}_t$ & state disturbance \\
% 	$\Sigma_e$ &state disturbance covariance matrix\\
% 	$\mathbf{\epsilon}_t$ & observation noise \\
% 	$\Sigma_{\epsilon}$ &observation noise covariance matrix\\
%     	$\mathbf{C}$ & observation matrix \\
% 	$c_{ij}$& elements of observation matrix
%     \end{tabular}
%     \caption{Decomposition}
% \end{table}
% 
% \begin{table}[h!]\footnotesize
%     \begin{tabular}{rl}
%         $V(\nu)$ & Spectrum of the dynamic field \\
% 	$\nu$ & Spatial frequency \\
% 	$\nu_c$ & Spatial cut-off frequency \\
% 	$\Delta_y$ & Distance between adjacent sensors \\
% 	$\rho$ & Over-sampling parameter \\
% 	$\Delta_{\phi}$ & Distance between field basis functions \\
% 	$\sigma_{\nu}^2$ & Variance of FT of Gaussian basis function \\
% 	$\sigma^2_{\phi}$ & Spatial variance of Gaussian in spatial domain \\
%     \end{tabular}
%     \caption{Frequency Analysis}
% \end{table}
% 
% \begin{table}[h!]\footnotesize
%     \begin{tabular}{ll}
%         $\hat{\mathbf{x}}$ & State estimate \\
% 	$\chi$ & Matrix of sigma vectors \\
% 	$\lambda$& Scaling parameter\\
% 	$\alpha$& Determines the spread of sigma points\\
% 	$\beta$& Prior knowledge of the sigma points distribution\\
% 	$\kappa$& Scaling parameter\\
% 	$W$& Sigma vecors weights\\
%     	$\hat{\mathbf{x}}_t^{f-}$ & Forward prior estimate \\
%     	$\hat{\mathbf{x}}_t^f$ & Forward posterior estimate \\
%     	$\hat{\mathbf{x}}_t^{b-}$ & Backward prior estimate \\
%     	$\hat{\mathbf{x}}_t^{b}$ & Backward posterior estimate \\
%     	$P^f_t$ & Forward posterior covariance matrix \\
%     	$P^{f-}_t$ & Forward prior covariance matrix \\
%     	$P^b_t$ & Backward posterior covariance matrix \\
%     	$P^{b-}_t$ & Backward prior covariance matrix \\
% 	$\mathcal K_{t} $& Filter gain\\
% 	$M_t$& Cross-covariance matrix\\
% 	$S_t$& Smoother gain
%     \end{tabular}
%     \caption{State Estimation}
% \end{table}

>>>>

\begin{table}[!ht]
\caption{
\bf{Notation and Parameters}}
\begin{tabular}{|c|l|c|c|}
	\hline
	\textbf{Symbol} & \textbf{Quantity} & \textbf{Value} & \textbf{Units}\\
	\hline
	\multicolumn{4}{|c|}{\emph{Domain and indices}}\\
	\hline
	$\Omega$ & spatial domain & &\\
	$\Delta$ & spatial discretisation step & 0.5 & mm \\
	$t$ & time & & s\\
	$\mathbf{r}$ & spatial location & &\\
	$n$ & sensor index $n=1,..,N$ & &\\
	$T_s$ & time step & $0.001$ & s\\
	$T$ & number of time steps & 0.4 & s\\
	\hline
	\multicolumn{4}{|c|}{\emph{Spatiotemporal signals}}\\
	\hline
    $y(\mathbf{r}_n,t)$ & observation & & mV\\
    $v(\mathbf{r},t)$ & mean membrane potential & & mV \\
	$g(\mathbf{r},t)$ & weighted firing rate function & & \\
	$f(\mathbf{r},t)$ & firing rate function & & spikes.s$^{-1}$\\
	$e(\mathbf{r},t)$ & field disturbance, (covariance $\gamma$) & &\\
	$\varepsilon(\mathbf{r}_n,t)$ & observation noise, (covariance $\Sigma_\varepsilon$) & &\\
	\hline 
\multicolumn{4}{|c|}{\emph{Model}}\\
	\hline
	$h(t)$ & post-synaptic response kernel & & mV\\
	$\tau$ & synaptic time constant & 0.01 & s$^{-1}$ \\
	$\zeta$ & inverse synaptic time constant & & s$^{-1}$\\
	$\xi$ & time constant parameter & & \\
	$\eta(t)$ & Heaviside step function & & \\
	$m(\mathbf{r},\mathbf{r}')$ & sensor kernel (width $\sigma_m^2$) & & \\
	$w(\mathbf{r},\mathbf{r}')$ & spatial connectivity kernel & & \\
	$f_{max}$ & maximal firing rate & & spikes.s$^{-1}$\\
	$\varsigma$ & slope of sigmoidal activation function & & \\
	$v_0$ & firing threshold & & mV \\
	$\delta(t)$ & Dirac-delta function & & \\
	$D$ & Temporal differential operator & &\\
	$\boldsymbol{\theta}$ & & $\left[\begin{array}{ccc}
	10 &-8 &0.5
	\end{array}
	\right]^{\top}$ & mV/spike\\
	$\sigma_{\psi_{1}}, \sigma_{\psi_{2}}, \sigma_{\psi_{3}}$ & & 1.8, 2.4, 6 & mm\\
	$\sigma_{m},\Delta_{y}$& & 0.9, 1.5 & mm\\
	$\Sigma_{\varepsilon}$ & & $0.1 \times I_{N}$ & mm$^2$ \\
	$\sigma_{\gamma}$& & 1.3 & mm\\
	\hline
\end{tabular}
\begin{flushleft}Table caption
\end{flushleft}
\label{tab:label}
\end{table}

% 	\hline
% 	\multicolumn{4}{|c|}{\emph{Decomposition}} \\
% 	\hline
%     $L$ & number of field basis functions & 81 & \\
%    	$\boldsymbol\phi(\mathbf{r})$ & vector of Gaussian basis functions & & \\
%    	$\mathbf{x}_t$ & state vector at time $t$ & & \\
%    	$\boldsymbol{\psi}$ & vector of connectivity kernel basis functions & & \\
%    	$\theta$ & vector of connectivity kernel parameters & & \\
%    	$\Gamma$ & inner product of field basis functions & &\\
%    	$q()$ & state function & &\\
%    	$Q()$ & state function & &\\
% 	$\gamma(\mathbf r-\mathbf r')$& field disturbance covariance function & &\\
%    	$\mathbf{e}_t$ & state disturbance & &\\
% 	$\Sigma_e$ &state disturbance covariance matrix& &\\
% 	$\mathbf{\epsilon}_t$ & observation noise & &\\
% 	$\Sigma_{\epsilon}$ &observation noise covariance matrix& &\\
%    	$\mathbf{C}$ & observation matrix& & \\
% 	$c_{ij}$& elements of observation matrix & & \\
% 	\hline
% \end{tabular}
% \begin{flushleft}Table caption
% \end{flushleft}
% \label{tab:label}
% \end{table}

\begin{table}[!ht]
\caption{
\bf{Notation and Parameters - Part 2}}
\begin{tabular}{|c|l|c|c|}
	\hline
	\textbf{Symbol} & \textbf{Quantity} & \textbf{Value} & \textbf{Units}\\
	\hline
	\multicolumn{4}{|c|}{\emph{Decomposition}} \\
	\hline
    $L$ & number of field basis functions & 81 & \\
   	$\boldsymbol\phi(\mathbf{r})$ & vector of Gaussian basis functions & & \\
   	$\mathbf{x}_t$ & state vector at time $t$ & & \\
   	$\boldsymbol{\psi}$ & vector of connectivity kernel basis functions & & \\
   	$\theta$ & vector of connectivity kernel parameters & & \\
   	$\Gamma$ & inner product of field basis functions & &\\
   	$q()$ & state function & &\\
   	$Q()$ & state function & &\\
	$\gamma(\mathbf r-\mathbf r')$& field disturbance covariance function & &\\
   	$\mathbf{e}_t$ & state disturbance & &\\
	$\Sigma_e$ &state disturbance covariance matrix& &\\
	$\mathbf{\varepsilon}_t$ & observation noise & &\\
	$\Sigma_{\varepsilon}$ &observation noise covariance matrix& &\\
   	$\mathbf{C}$ & observation matrix& & \\
	$c_{ij}$& elements of observation matrix & & \\
	\hline
	\multicolumn{4}{|c|}{\emph{Frequency Analysis}} \\
	\hline
    $V(\nu)$ & Spectrum of the dynamic field & &\\
	$\nu$ & Spatial frequency & &\\
	$\nu_c$ & Spatial cut-off frequency & &\\
	$\Delta_y$ & Distance between adjacent sensors & &\\
	$\rho$ & Over-sampling parameter & &\\
	$\Delta_{\phi}$ & Distance between field basis functions & &\\
	$\sigma_{\nu}^2$ & Variance of FT of Gaussian basis function & &\\
	$\sigma^2_{\phi}$ & Spatial variance of Gaussian in spatial domain & &\\
	\hline
	\multicolumn{4}{|c|}{\emph{State Estimation}} \\
	\hline
	$\chi$ & Matrix of sigma vectors & &\\
	$\lambda$& Scaling parameter & &\\
	$\alpha$& Determines the spread of sigma points & &\\
	$\beta$& Prior knowledge of the sigma points distribution & &\\
	$\kappa$& Scaling parameter & & \\
	$W$& Sigma vecors weights & & \\
   	$\hat{\mathbf{x}}_t^{f-}$ & Forward prior estimate & & \\
   	$\hat{\mathbf{x}}_t^f$ & Forward posterior estimate & & \\
   	$\hat{\mathbf{x}}_t^{b-}$ & Backward prior estimate & & \\
   	$\hat{\mathbf{x}}_t^{b}$ & Backward posterior estimate & & \\
   	$P^f_t$ & Forward posterior covariance matrix & & \\
   	$P^{f-}_t$ & Forward prior covariance matrix & & \\
   	$P^b_t$ & Backward posterior covariance matrix & & \\
   	$P^{b-}_t$ & Backward prior covariance matrix & & \\
	$\mathcal K_{t} $& Filter gain & & \\
	$M_t$& Cross-covariance matrix & & \\
	$S_t$& Smoother gain & & \\	
	\hline
\end{tabular}
\begin{flushleft}Table caption
\end{flushleft}
\label{tab:label}
\end{table}

@@

\begin{table}[h!]\footnotesize
    \begin{tabular}{ll}
        $\hat{\mathbf{x}}$ & State estimate \\
	$\chi$ & Matrix of sigma vectors \\
	$\lambda$& Scaling parameter\\
	$\alpha$& Determines the spread of sigma points\\
	$\beta$& Prior knowledge of the sigma points distribution\\
	$\kappa$& Scaling parameter\\
	$W$& Sigma vecors weights\\
    	$\hat{\mathbf{x}}_t^{f-}$ & Forward prior estimate \\
    	$\hat{\mathbf{x}}_t^f$ & Forward posterior estimate \\
    	$\hat{\mathbf{x}}_t^{b-}$ & Backward prior estimate \\
    	$\hat{\mathbf{x}}_t^{b}$ & Backward posterior estimate \\
    	$P^f_t$ & Forward posterior covariance matrix \\
    	$P^{f-}_t$ & Forward prior covariance matrix \\
    	$P^b_t$ & Backward posterior covariance matrix \\
    	$P^{b-}_t$ & Backward prior covariance matrix \\
	$\mathcal K_{t} $& Filter gain\\
	$M_t$& Cross-covariance matrix\\
	$S_t$& Smoother gain
    \end{tabular}
    \caption{State Estimation}
\end{table}
